Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-08-21 Paper/gammaRays.tex
Renamed Discussion to Summary
Also corrections to summary
Fixed zmax=180 -> zmax=100 in paper
Corrections to code upcoming

\texttt{gtpsf}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtpsf.txt}} tool requires the livetime map to generate the PSFs. This map is computed by \texttt{gtltcube}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtltcube.txt}} with the following parameters:
\begin{lstlisting}
gtltcube evfile=timed.fits evtable=EVENTS scfile=[spacecraft] sctable=SC_DATA
	outfile=ltcube.fits
	dcostheta=0.025 binsz=1 phibins=0 tmin=0 tmax=0 zmax=180 zmin=0
\end{lstlisting}

@@

\section{Discussion}

\label{sec:discussion}

	The main results of our study may be summarized as following:
	\begin{enumerate}
		\item{
			The time stretching of GRB light curves between different VHE bands is confirmed with statistical significance of $3.3\sigma$.
		}
		\item{
			This time stretching can be explained by geometry of the jet, without introducing any new spectral components.
		}
		\item{
			All GRBs can be assumed to be the same in their rest frames.
			There is no need to vary internal burst parameters.
		}
	\end{enumerate}

>>>>

\texttt{gtpsf}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtpsf.txt}} tool requires the livetime map to generate the PSFs. This map is computed by \texttt{gtltcube}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtltcube.txt}} with the following parameters:
\begin{lstlisting}
gtltcube evfile=timed.fits evtable=EVENTS scfile=[spacecraft] sctable=SC_DATA
	outfile=ltcube.fits
	dcostheta=0.025 binsz=1 phibins=0 tmin=0 tmax=0 zmax=100 zmin=0
\end{lstlisting}

@@

\section{Summary}

\label{sec:summary}

	The main results of our study may be summarized as following:
	\begin{enumerate}
		\item{
			Time stretching of GRB light curves between different VHE bands is discovered with statistical significance of $3.3\sigma$.
		}
		\item{
			This time stretching can be explained by geometry of the jet, without introducing any new spectral components.
		}
		\item{
			All GRBs can be assumed to be the same in their rest frames.
			There is no need to vary internal burst parameters.
		}
	\end{enumerate}
